---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center",
  out.width = "70%",
  warning = FALSE
)
```

# timevarcorr

<!-- badges: start -->
[![Lifecycle:
experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN
status](https://www.r-pkg.org/badges/version/fw)](https://CRAN.R-project.org/package=timevarcorr)
<!-- badges: end -->

This R package is at a very early stage of development.
Many key features are missing (e.g. confidence intervals and test) and it may be buggy.
I also don't understand much of the statistical concepts involved.
So, please only use at your own risk.

It aims at computing the correlation between 2 time-series.
It performs a non-parametric kernel smoothing (using a common bandwidth) of all underlying components required for the computation of a correlation coefficient (i.e. $x$, $y$, $x^2$, $y^2$, $x*y$).
An automatic selection procedure for the bandwidth parameter is implemented.
Epanechnikov, Gaussian, and box kernels can be used.
Both Pearson and Spearman correlation coefficients can be estimated.


## Installation

You can install the development version of timevarcorr from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes") ## uncomment and run if you don't have this package installed
remotes::install_github("courtiol/timevarcorr")
```

That should suffice!

Note that this package relies so far on only one direct dependency -- [lpridge](https://github.com/cran/lpridge) -- which itself depends on nothing but a plain R install.

Nonetheless, in some of the examples below, I also rely on the [tidyverse](https://github.com/tidyverse) ecosystem, so you would need to install this as well to reproduce the content of this README:

``` r
install.packages("tidyverse")
```


## Examples

The main function of this package is called `tcor` and its documentation is available here:

```{r help}
help(tcor, package = timevarcorr)
```

Simple example using base-R syntax:

```{r example}
library(timevarcorr)

d <- stockprice[1:500, ]
test <- with(d, tcor(x = SP500, y = FTSE100, t = DateID, kernel = "normal"))
plot(test, type = "l", ylab = "Correlation", xlab = "Time", main = "SP500 vs FTSE100", las = 1)
```

Same example using tidyverse syntax:

```{r example2, message=FALSE}
library(tidyverse)

stockprice |> 
  slice(1:500) |>
  summarise(tcor(x = SP500, y = FTSE100, t = DateID, kernel = "normal")) |>
  ggplot() +
    aes(x = t, y = r) +
    geom_line() +
    labs(title = "SP500 vs FTSE100", x = "Time", y = "Correlation") +
    theme_classic()
```

Alternative using `dplyr::mutate` showing gaps of observations in the series:

```{r example3}
stockprice |> 
  slice(1:500) |>
  mutate(r = tcor(x = SP500, y = FTSE100, t = DateID, kernel = "normal", keep.missing = TRUE)$r) |>
  ggplot() +
    aes(x = DateID, y = r) +
    geom_line() +
    labs(title = "SP500 vs FTSE100", x = "Time", y = "Correlation") +
    theme_classic()
```

You can do more. For example, you can use other kernels, fix the bandwidth manually, or use the Spearman's rather than the Pearson's correlation coefficient:

```{r example4}
test2 <- with(d, tcor(x = SP500, y = FTSE100, t = DateID,
                      cor.method = "spearman", kernel = "box", h = 10))
plot(test2, type = "l", ylab = "Correlation (Spearman)", xlab = "Time", las = 1)
```


## Inspiration

The inspiration for this work was the reading of the following paper:

Choi, JE., Shin, D.W. Nonparametric estimation of time varying correlation coefficient. J. Korean Stat. Soc. 50, 333–353 (2021). https://doi.org/10.1007/s42952-020-00073-6


## Devel corner

README file compiled using `devtools::build_readme()`, with the following setup:

```{r sessioninfo}
devtools::session_info()
```


