---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center",
  out.width = "70%",
  warning = FALSE
)
```

# timevarcorr

<!-- badges: start -->
[![Lifecycle:
experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN
status](https://www.r-pkg.org/badges/version/fw)](https://CRAN.R-project.org/package=timevarcorr)
<!-- badges: end -->

This R package is at a very early stage of development.
Some key features are missing (e.g. tests) and it has not been thoroughly tested.
So, please only use at your own risk.

It aims at computing the correlation between 2 time-series following the method described in the following paper:

Choi, JE., Shin, D.W. Nonparametric estimation of time varying correlation coefficient. J. Korean Stat. Soc. 50, 333–353 (2021). https://doi.org/10.1007/s42952-020-00073-6

The chief idea is to perform a non-parametric kernel smoothing (using a common bandwidth) of all underlying components required for the computation of a correlation coefficient (i.e. $x$, $y$, $x^2$, $y^2$, $x*y$).

The automatic selection procedure for the bandwidth parameter proposed in the paper is implemented in this package.
The same goes for the computation of confidence intervals.

We also implemented the possibility to use Epanechnikov, Gaussian, or box kernels, as well as to estimate either the Pearson or the Spearman correlation coefficient.


## Installation

You can install the development version of timevarcorr from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes") ## uncomment and run if you don't have this package installed
remotes::install_github("courtiol/timevarcorr")
```

That should suffice!

Note that this package relies so far on only one direct dependency -- [lpridge](https://github.com/cran/lpridge) -- which itself depends on nothing but a plain R install.

Nonetheless, in some of the examples below, I also rely on the [tidyverse](https://github.com/tidyverse) ecosystem, so you would need to install this as well to reproduce the content of this README:

``` r
install.packages("tidyverse")
```


## Examples

The main function of this package is called `tcor` and its documentation is available here:

```{r help}
help(tcor, package = timevarcorr)
```

Simple example using base-R syntax:

```{r example}
library(timevarcorr)

d <- stockprice[1:500, ]
test <- with(d, tcor(x = SP500, y = FTSE100, t = DateID, kernel = "normal"))
plot(test, type = "l", ylab = "Correlation", xlab = "Time", main = "SP500 vs FTSE100", las = 1)
```

Same example using tidyverse syntax (with confidence interval):

```{r example2, message=FALSE}
library(tidyverse)

stockprice |> 
  slice(1:500) |>
  summarise(tcor(x = SP500, y = FTSE100, t = DateID, kernel = "normal", CI = TRUE)) |>
  ggplot() +
    aes(x = t, y = r, ymin = lwr, ymax = upr) +
    geom_ribbon(fill = "grey") +
    geom_line() +
    labs(title = "SP500 vs FTSE100", x = "Time", y = "Correlation") +
    theme_classic()
```

Alternative using `dplyr::mutate` showing gaps of observations in the series:

```{r example3}
stockprice |> 
  slice(1:500) |>
  mutate(r = tcor(x = SP500, y = FTSE100, t = DateID, kernel = "normal", keep.missing = TRUE)$r) |>
  ggplot() +
    aes(x = DateID, y = r) +
    geom_line() +
    labs(title = "SP500 vs FTSE100", x = "Time", y = "Correlation") +
    theme_classic()
```

You can do more. For example, you can use other kernels, fix the bandwidth manually, or use the Spearman's rather than the Pearson's correlation coefficient:

```{r example4}
test2 <- with(d, tcor(x = SP500, y = FTSE100, t = DateID,
                      cor.method = "spearman", kernel = "box", h = 10))
plot(test2, type = "l", ylab = "Correlation (Spearman)", xlab = "Time", las = 1)
```


## Devel corner

README file compiled using `devtools::build_readme()`, with the following setup:

```{r sessioninfo}
devtools::session_info()
```


