---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%"
)
```

# timevarcorr

<!-- badges: start -->
[![Lifecycle:
experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN
status](https://www.r-pkg.org/badges/version/fw)](https://CRAN.R-project.org/package=timevarcorr)
<!-- badges: end -->

This R package is at a very early stage of development.
Many features are missing and it may be buggy.
Use at your own risk.

It aims at computing the correlation between 2 time-series.
It performs a non-parametric kernel smoothing (using a common bandwidth) of all underlying componenents required for the computation of a correlation coefficient (i.e. $x$, $y$, $x^2$, $y^2$, $x*y$).
An automatic selection procedure for the bandwidth parameter is implemented.
Gaussian, box and Epanechnikov kernels can be used.
Both Pearson and Spearman correlation coefficients can be estimated.


## Installation

You can install the development version of timevarcorr from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("courtiol/timevarcorr")
```

## Example

Simple example using base-R syntax:

```{r example}
library(timevarcorr)
d <- stockprice[1:500, ]
test <- with(d, tcor(x = SP500, y = FTSE100, t = DateID, kernel = "normal"))
plot(test, type = "l", ylab = "Correlation", xlab = "Time", main = "SP500 vs FTSE100", las = 1)
```

Same example using tidyverse syntax:

```{r example2}
library(tidyverse)

stockprice |> 
  slice(1:500) |>
  summarise(tcor(x = SP500, y = FTSE100, t = DateID, kernel = "normal")) |>
  ggplot() +
    aes(x = t, y = r) +
    geom_line() +
    labs(title = "SP500 vs FTSE100", x = "Time", y = "Correlation") +
    theme_classic()
```

Alternative using `dplyr::mutate` showing gaps of observations in the series:

```{r example3}
stockprice |> 
  slice(1:500) |>
  mutate(r = tcor(x = SP500, y = FTSE100, t = DateID, kernel = "normal", keep.missing = TRUE)$r) |>
  ggplot() +
    aes(x = DateID, y = r) +
    geom_line() +
    labs(title = "SP500 vs FTSE100", x = "Time", y = "Correlation") +
    theme_classic()
```

You can do more. For exampe, you can use other kernels, fix the bandwidth manually, or use the Spearman's rather than the Pearson's correlation coefficient:

```{r example4}
test2 <- with(d, tcor(x = SP500, y = FTSE100, t = DateID, cor.method = "spearman", kernel = "box", h = 10))
plot(test2, type = "l", ylab = "Correlation (Spearman)", xlab = "Time", las = 1)
```

## Inspiration

The inspiration for this work was the reading of the following paper:

Choi, JE., Shin, D.W. Nonparametric estimation of time varying correlation coefficient. J. Korean Stat. Soc. 50, 333–353 (2021). https://doi.org/10.1007/s42952-020-00073-6


